### 2021-04-29 sections/queueing_model/main.tex
Apply minor edits

\begin{itemize}
    \item $\lambda_1$: The arrival rate of class 1 individuals
    \item $\lambda_2$: The arrival rate of class 2 individuals
    \item $\mu$: The service rate for individuals receiving service in waiting 
    zone 1
    \item $C$: The number of servers
    \item $T$: The threshold where class 2 individuals will start being blocked 
\end{itemize}

@@

Note that $\Lambda$ here denotes the overall arrival rate in the model by both 
classes of individuals (i.e. $\Lambda = \lambda_1 + \lambda_2$). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general-markov-model}.

>>>>

\begin{itemize}
    \item \(\lambda_1\): The arrival rate of class 1 individuals
    \item \(\lambda_2\): The arrival rate of class 2 individuals
    \item \(\mu\): The service rate for individuals receiving service in waiting 
    zone 1
    \item \(C\): The number of servers
    \item \(T\): The threshold where class 2 individuals will start being blocked 
\end{itemize}

@@

Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
classes of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general-markov-model}.
